---
title: "Preprocess_sans_trans"
author: "Chelsea Bihlmeyer"
date: "2026-04-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE, message=FALSE}
# === CHUNK 1: Libs & Config ===
library(jsonlite)
library(dplyr)
library(purrr)
library(tidyr)
library(stringr)
library(readr)
library(readxl)

ZEESCHUIMER_PATH <- "zeeschuimer-export.ndjson" 
```

```{r, warning=FALSE, message=FALSE}
# === CHUNK 2.1: Load & Flatten ===
# "jsonlite::stream_in" handles NDJSON/JSONL line-by-line when using file() with pagesize
##  by using a connection + stream_in(), you’re set up to parse .ndjson / .jsonl cleanly and efficiently, and you can control batch size with pagesize if needed. Safer for big files.
con <- file(ZEESCHUIMER_PATH, open = "r") # Opens a read-only connection to NDJSON/JSONL file.
# on.exit(close(con)) # Deferred close the connection
raw_list <- stream_in(con, verbose = FALSE) # Each line becomes one record; bound row-wise
```

```{r}
# === CHUNK 2.2: Load & Flatten ===
meta <- as_tibble(raw_list)
```

```{r}
# === CHUNK 2.3: Load & Flatten ===
## Step: Widen the packed data column (only). 
## Turns inner columns of "data" into top-level columns with the prefix "data"

# Already have: meta <- as_tibble(raw_list) from CHUNK 2.2
# Safety check: confirm `data` is a data.frame column
stopifnot(is.data.frame(meta$data))

# Unnest just the first level: expand inner columns to top-level with a prefix
meta <- meta %>%
  unnest_wider(data, names_sep = ".")

# Quick peek to verify outcome
names(meta)[1:40]        # skim first ~40 names
str(meta, max.level = 1) # confirm list-cols (author, video, stats, etc.) still present but top-level
```


```{r}
# === CHUNK 2.3, con't: Load & Flatten ===
## Step: Next-level extraction
## Unnest: item_id, createTime, desc_raw, and is_ad_platform
## Keep all the list‑columns (data.author, data.stats, data.textExtra, etc.) untouched for the following steps.

# Surface the most-used scalar fields; keep nested list-cols as-is for now
meta <- meta %>%
  mutate(
    item_id        = dplyr::coalesce(.data[["item_id"]], .data[["data.id"]]),
    item_id = as.character(item_id),
    createTime     = .data[["data.createTime"]],
    desc_raw       = .data[["data.desc"]],
    is_ad_platform = dplyr::coalesce(.data[["data.isAd"]], FALSE)
  )
```


```{r}
# === CHUNK 2.3, con't: Load & Flatten ===
## Step: Next-level extraction
## Un‑nest data.author to expose two author identifier columns: author_id and author_handle

# Safety check: the column exists and is list-like
stopifnot("data.author" %in% names(meta))

# Controlled widen of just the `author` sub-object
meta <- meta %>%
  unnest_wider(col = data.author, names_sep = "." , names_repair = "unique")
# Resulting columns should include: data.author.id, data.author.uniqueId, etc.

# Safety check, all variables with prefix "data.author"
grep("^data\\.author\\.", names(meta), value = TRUE)

# Surface feature-map fields author_id and author_handle 
meta <- meta %>%
  mutate(
    author_id      = .data[["data.author.id"]],
    author_id = as.character(author_id),
    author_handle  = .data[["data.author.uniqueId"]]
  )


# Safety check, author_id and author_handle
meta %>% select(item_id, author_id, author_handle) %>% head(3)
sum(is.na(meta$author_id))
# looks good! no NA
```


```{r}
# === CHUNK 2.3, con't: Load & Flatten ===
## Step: Next-level extraction
## Un‑nest data.stats to expose engagement metrics: "diggs" (likes), shares, comments, plays, "collects" (shares)
## In later steps, use Engage_* columns via coalesce() data.statsv2 as a fallback

# 1) Widen ONLY data.stats into top-level columns with a clear prefix.
meta <- meta %>%
  unnest_wider(`data.stats`, names_sep = ".", names_repair = "unique")

# 2) Create the engagement columns from data.stats (no fallback to statsv2 yet).
meta <- meta %>%
  mutate(
    engage_likes    = suppressWarnings(as.numeric(.data[["data.stats.diggCount"]])),
    engage_shares   = suppressWarnings(as.numeric(.data[["data.stats.shareCount"]])),
    engage_comments = suppressWarnings(as.numeric(.data[["data.stats.commentCount"]])),
    engage_plays    = suppressWarnings(as.numeric(.data[["data.stats.playCount"]])),
    engage_saves    = suppressWarnings(as.numeric(.data[["data.stats.collectCount"]]))
  )
```


```{r}
# === CHUNK 2.3, con't: Load & Flatten ===
## Step: Next-level extraction
## Un‑nest data.statsv2 as a fallback
## Engagement metrics: "diggs" (likes), shares, comments, plays, "collects" (shares)
## Use Engage_* columns via coalesce() stats and statsv2 

# 1) Widen ONLY data.statsV2 into top-level columns with a clear prefix (if present).
if ("data.statsV2" %in% names(meta)) {
  meta <- meta %>%
    unnest_wider(`data.statsV2`, names_sep = ".", names_repair = "unique")
}
# 2) Coalesce the final engage_* fields to prefer stats (already computed),
#    and fall back to statsV2 when available.
#    Guard each reference so we don't error if a V2 column is absent.
meta <- meta %>%
  mutate(
    engage_likes    = dplyr::coalesce(
                        engage_likes,
                        if ("data.statsV2.diggCount"    %in% names(.)) suppressWarnings(as.numeric(.data[["data.statsV2.diggCount"]]))    else NA_real_
                      ),
    engage_shares   = dplyr::coalesce(
                        engage_shares,
                        if ("data.statsV2.shareCount"   %in% names(.)) suppressWarnings(as.numeric(.data[["data.statsV2.shareCount"]]))   else NA_real_
                      ),
    engage_comments = dplyr::coalesce(
                        engage_comments,
                        if ("data.statsV2.commentCount" %in% names(.)) suppressWarnings(as.numeric(.data[["data.statsV2.commentCount"]])) else NA_real_
                      ),
    engage_plays    = dplyr::coalesce(
                        engage_plays,
                        if ("data.statsV2.playCount"    %in% names(.)) suppressWarnings(as.numeric(.data[["data.statsV2.playCount"]]))    else NA_real_
                      ),
    engage_saves    = dplyr::coalesce(
                        engage_saves,
                        if ("data.statsV2.collectCount" %in% names(.)) suppressWarnings(as.numeric(.data[["data.statsV2.collectCount"]])) else NA_real_
                      )
  )
```


```{r}
# === CHUNK 2.3, Load & Flatten (RAW only, exportable) ===
## Step: Next-level extraction
## Un‑nest hashtag list from data.textExtra
## Output in this chunk:
##   - hashtags_list_raw : list<character> (kept for cleaning in next chunk)
##   - hashtags_raw      : character JSON array string (exportable)

.extract_hashtags <- function(x) {
  # Empty → empty vector
  if (is.null(x)) return(character(0))
  
  # Helper to pull hashtagName / hashtag_name from any list/data.frame
  pull_vals <- function(obj) {
    if (is.null(obj)) return(NULL)
    if (is.list(obj) || is.data.frame(obj)) {
      v <- obj[["hashtagName"]]
      if (is.null(v)) v <- obj[["hashtag_name"]]  # occasional alternate key
      return(v)
    }
    if (is.character(obj)) return(obj)            # very rare: raw chars
    NULL
  }
  
  vals <- NULL
  if (is.data.frame(x)) {
    # Packed df: the column itself might be atomic or a list-column
    vals <- pull_vals(x)
  } else if (is.list(x)) {
    # List of entries: pull from each and combine
    vals <- lapply(x, pull_vals)
  } else {
    return(character(0))
  }
  
  # Flatten to a simple character vector (NO cleaning here)
  out <- unlist(vals, recursive = TRUE, use.names = FALSE)
  out <- as.character(out)
  out <- out[!is.na(out) & nzchar(out)]
  out
}
# Apply to each row; produce both list-col (for next chunk) and exportable char col
meta <- meta %>%
  dplyr::mutate(
    hashtags_list_raw = purrr::map(`data.textExtra`, .extract_hashtags),
    hashtags_raw = purrr::map_chr(
      hashtags_list_raw,
      ~ if (length(.x) == 0) "[]" else jsonlite::toJSON(.x, auto_unbox = TRUE)
    )
  )
```


```{r}
# === Sanity Check Hashtags ===
# How many posts have any hashtags?
sum(purrr::map_int(meta$hashtags_list_raw, length) > 0)

# How many hashtags in the first few rows/IDs/videos?
purrr::map_int(meta$hashtags_list_raw[1:10], length)

# Show the actual hashtag vectors for the first few rows with any hashtags
first_with_tags <- which(purrr::map_int(meta$hashtags_raw, length) > 0)[1:3]
meta$hashtags_raw[first_with_tags]
```


```{r}
# === CHUNK 2.3, con't: Load & Flatten ===
## Step: Next-level extraction
## Duration and audio

########
##### DURATION in secs ##### 
# Widen ONLY data.video for duration
meta <- meta %>%
  unnest_wider(`data.video`, names_sep = ".", names_repair = "unique")

# Extract duration as numeric; no transform
meta <- meta %>%
  mutate(
    duration_s = suppressWarnings(as.numeric(.data[["data.video.duration"]]))
  )

# Examine the duration column
meta %>% select(item_id, duration_s) %>% head(15)
summary(meta$duration_s)

########
##### TEXT LANG ##### 
# Create text_lang directly from data.textLanguage (no transforms)
meta <- meta %>%
  mutate(
    text_lang = as.character(.data[["data.textLanguage"]])
  )

# Verification
# Confirm presence and peek
"text_lang" %in% names(meta)
head(meta$text_lang, 10)

# How many are non-empty?
sum(!is.na(meta$text_lang) & nzchar(meta$text_lang))

########
##### ORIGINAL AUDIO FLAG ##### 
# Widen ONLY the music subobject (no other fields touched)
meta <- meta %>%
  unnest_wider(`data.music`, names_sep = ".", names_repair = "unique")

# Minimal extraction: direct copy of the boolean flag
## If the column is absent for some rows/scrapes,  keep NA
if ("data.music.original" %in% names(meta)) {
  meta <- meta %>%
    mutate(audio_original_flag = .data[["data.music.original"]])
} else {
  meta <- meta %>%
    mutate(audio_original_flag = NA)

}
# Original Audio Checks

# Confirm the new column exists and inspect distribution
"audio_original_flag" %in% names(meta)
table(meta$audio_original_flag, useNA = "ifany")

# Spot-check a few rows
meta %>% select(item_id, audio_original_flag) %>% head(5)

########
##### AUDIO LOUDNESS ##### 

meta <- meta %>%
  unnest_wider(`data.video.volumeInfo`, names_sep = ".", names_repair = "unique")

# Build a prioritized list of candidate column names (common schema variants)
candidates <- c(
  "data.video.volumeInfo.Loudness",
  "data.video.volumeInfo.loudness",
  "data.volumeInfo.Loudness",
  "data.volumeInfo.loudness"
)
# Keep only those that are present in `meta`
present <- candidates[candidates %in% names(meta)]

# Assign using the first present candidate; otherwise set NA_real_
if (length(present) > 0) {
  chosen <- present[1]
  meta <- meta %>%
    mutate(audio_loudness_LUFs = suppressWarnings(as.numeric(.data[[chosen]])))
} else {
  meta <- meta %>%
    mutate(audio_loudness_LUFs = NA_real_)
}
# Check Audio Loundess
"audio_loudness_LUFs" %in% names(meta)
meta %>% select(item_id, audio_loudness_LUFs) %>% head(5)
summary(meta$audio_loudness_LUFs)
sum(!is.na(meta$audio_loudness_LUFs))


```

At this step, in CHUNK 2.3, the following fields were "widened" ("un-nested"/"extracted") and now appear as column variables:

IDs/handles (item_id, author_id, author_handle)
Core text surface (desc_raw)
Engagement (engage_*) with statsV2 fallback
Hashtags (hashtags_list_raw)
Time source (createTime, untransformed)
Ad flag (is_ad_platform)
Duration (duration_s)
Text language (text_lang)
Audio flags/metrics (audio_original_flag, audio_loudness_db)

Importantly, no transformations were required for these variables. There were simply, essentially, "copy-and-paste" from the scraped metadata.

Now, in the steps below (CHUNK 3), duplicate videos will be removed.

################################

De-Duping

################################

```{r}
# === CHUNK 3.1, Identify Duplicate Item ID ===

# How many total rows vs. distinct item_id?
data.frame(
  total_rows    = nrow(meta),
  distinct_ids  = dplyr::n_distinct(meta$item_id)
)

# Which item_id values are duplicated, and how many times?
dup_ids <- meta%>%
  count(item_id, name = "n") %>%
  filter(n > 1) %>%
  arrange(desc(n))
```


```{r}
# === CHUNK 3.2, Drop Duplicate Item ID ===
############# DROP DUPLICATE ITEM_ID #############

# Keep the first occurrence of each item_id
meta_dedup <- meta %>%
  distinct(item_id, .keep_all = TRUE)

# Quick confirmation
data.frame(
  rows_before = nrow(meta),
  rows_after  = nrow(meta_dedup),
  distinct_ids = dplyr::n_distinct(meta_dedup$item_id)
)
```

################################

On-screen text

################################


```{r}
# === CHUNK 4.1, Capture On-Screen Text  ===

# Helper: safely coerce a stickers object to a data frame and extract candidate text fields
extract_sticker_texts <- function(x) {
  # Normalize empty/NA cases
  if (is.null(x) || length(x) == 0 || (length(x) == 1 && is.na(x))) {
    return(character(0))
  }
  # Try to coerce to a data frame of stickers
  df <- tryCatch(
    {
      # If x is already a data.frame / tibble OR a list of records, bind_rows handles both
      dplyr::bind_rows(x)
    },
    error = function(e) {
      # If coercion fails, return empty char vector
      tibble::tibble()
    }
  )

  if (nrow(df) == 0) return(character(0))
  
   # Candidate fields: primary 'stickerText', fallback 'text'
  vals <- character(0)
  if ("stickerText" %in% names(df)) vals <- c(vals, df$stickerText)
  if ("text"        %in% names(df)) vals <- c(vals, df$text)

  # Clean minimal: keep as-is (no normalization yet), just trim and drop empties
  vals <- vals[!is.na(vals)]
  vals <- as.character(vals)
  vals <- str_trim(vals)
  vals <- vals[nzchar(vals)]

  vals
}

# ---- Perform the extraction on meta_dedup (row order preserved) ----
meta_dedup <- meta_dedup %>%
  mutate(
    .stickers_raw   = `data.stickersOnItem`,
    .texts_list     = map(.stickers_raw, extract_sticker_texts),
    # on_screen_text_present = map_lgl(.texts_list, ~ length(.x) > 0),
    on_screen_text_text    = map_chr(.texts_list, ~ if (length(.x) == 0) NA_character_ else paste(.x, collapse = "\n"))
  ) %>%
  select(-.stickers_raw, -.texts_list)

# ---- Minimal preview ----

# 1) Frequency table of on_screen_text_text
# table(meta_dedup$on_screen_text_present)

# 2) First 5 rows where TRUE with item_id + on_screen_text_text
meta_dedup %>%
  select(item_id, on_screen_text_text) %>%
  head(5)
```

################################

Text Cleaning

################################

Now, in the steps below (CHUNK 5), createTime, hasthags, on-screen text, and description  will be cleaned.

```{r}
# === CHUNK 5.1, Clean & Normalize Time ===
## Step: createTime → post_time_utc transform
## Unix → UTC datetime

meta_dedup <- meta_dedup %>%
  mutate(
    # 1) Coerce to numeric safely (handles character digits)
    createTime_num = suppressWarnings(as.numeric(createTime)),

    # 2) Normalize to seconds since epoch
    #    - typical TikTok web JSON uses seconds (10 digits)
    #    - some exports use milliseconds (13 digits)
    createTime_s = case_when(
      is.na(createTime_num) ~ NA_real_,
      createTime_num > 1e12 ~ createTime_num / 1000,  # ms → s
      createTime_num > 1e10 ~ createTime_num / 1000,  # defensive guard
      TRUE                  ~ createTime_num          # already seconds
    ),

    # 3) Final UTC timestamp
    post_time_utc = as.POSIXct(createTime_s, origin = "1970-01-01", tz = "UTC")
  )
```



```{r}
# === CHUNK 5.0, Helpers to Clean & Normalize ===

# ---- Emoji pattern (define once if not already present) ----
if (!exists("emoji_pat", inherits = FALSE)) {
  emoji_pat <- paste0(
    "(?:",
      # keycap emoji like 1️⃣, #️⃣, *️⃣
      "(?:[\\#\\*0-9]\\uFE0F?\\u20E3)",
      "|(?:\\p{RI}{2})",             # flags 🇺🇸 etc.
      "|\\p{Emoji_Presentation}",     # default-emoji characters
      "|\\p{Extended_Pictographic}",  # pictographs that render as emoji
    ")"
  )
}

# ---- HTML entity unescape (2-pass to handle double-encoded entities) ----
unescape_entities <- function(x) {
  if (is.null(x)) return(x)
  x <- as.character(x)
  # Pass 1: collapse over-encoded forms (e.g., &amp;amp; -> &amp;)
  x <- str_replace_all(
    x,
    c("&amp;amp;"="&amp;","&amp;lt;"="&lt;","&amp;gt;"="&gt;","&amp;quot;"="\"","&amp;#39;"="'")
  )
  # Pass 2: decode remaining
  x <- str_replace_all(
    x,
    c("&amp;"="&","&lt;"="<","&gt;"=">","&quot;"="\"","&#39;"="'")
  )
  x
}

# ---- Normalize curly quotes/apostrophes to ASCII (avoid CSV mojibake) ----
normalize_ascii_quotes <- function(x) {
  x %>%
    str_replace_all("[\\u2018\\u2019]", "'") %>%  # ‘ ’ -> '
    str_replace_all("[\\u201C\\u201D]", "\"")     # “ ” -> "
}

# ---- Remove zero-width characters ----
strip_zero_width <- function(x) {
  str_replace_all(x, "[\\u200B-\\u200D\\uFEFF]", "")
}

# ---- Replace URLs with placeholder ----
replace_urls_with_placeholder <- function(x, placeholder = " __URL__ ") {
  str_replace_all(x, "https?://\\S+", placeholder)
}

# ---- Remove hashtag tokens (avoid nuking HTML entities like &#) ----
strip_hashtag_tokens <- function(x) {
  str_replace_all(x, "(?<!&)#\\S+", " ")
}

# ---- Remove @mentions ----
strip_mentions <- function(x) {
  str_replace_all(x, "@\\S+", " ")
}

# ---- Remove emojis ----
strip_emojis <- function(x) {
  stringi::stri_replace_all_regex(x, emoji_pat, "")
}

# ---- Extract emojis: for character vectors (one string per row) ----
extract_emojis_char <- function(x) {
  res <- stringi::stri_extract_all_regex(x, emoji_pat)
  purrr::map_chr(res, ~ if (length(.x) == 0 || all(is.na(.x))) NA_character_ else paste(.x, collapse = " "))
}

# ---- Restrict punctuation: keep only contraction apostrophes, in-word hyphens, and sentence-final periods
restrict_punct_keep_contracts_hyphens_sentence_periods <- function(x) {
  if (is.null(x)) return(x)
  x <- as.character(x)

  # Normalize Unicode dash variants to ASCII hyphen for consistent handling
  # figure dash (U+2012), en dash (U+2013), em dash (U+2014), horizontal bar (U+2015)
  x <- stringr::str_replace_all(x, "[\u2012\u2013\u2014\u2015]", "-")

  # --- PERIODS ---
  # Convert trailing "..." (or more) into a single sentence-final period first
  x <- stringr::str_replace_all(
    x,
    "(?<=\\w)\\.{2,}(?=(?:[\"')\\]]*\\s|[\"')\\]]*$))",
    "."
  )

  # Mark sentence-final periods we want to keep:
  # Definition: a '.' that follows a word char and is then followed by optional closing quotes/brackets and
  # either whitespace or end-of-string.
  x <- stringr::str_replace_all(
    x,
    "(?<=\\w)\\.(?=(?:[\"')\\]]*\\s|[\"')\\]]*$))",
    "<<<KEEP_DOT>>>"
  )

  # Remove *all other* periods, including abbreviation/decimal dots
  x <- stringr::str_replace_all(x, "\\.", "")

  # Restore the sentence-final periods
  x <- stringr::str_replace_all(x, "<<<KEEP_DOT>>>", ".")

  # --- APOSTROPHES ---
  # Preserve apostrophes *only* when both neighbors are letters (i.e., genuine contractions like don't, I'm).
  # Everything else (leading/trailing quotes, possessives like John's, decade forms like '90s) is removed.
  # Remove apostrophes not surrounded by letters:
  x <- stringr::str_replace_all(x, "(?<!\\p{L})'|'(?!\\p{L})", "")

  # --- HYPHENS ---
  # Keep hyphens only when they hyphenate words (word char on both sides).
  # Replace other hyphens with a space (so tokens don't glue together).
  x <- stringr::str_replace_all(x, "(?<!\\w)-(?!\\w)", " ")

  # --- OTHER PUNCTUATION / SYMBOLS ---
  # Remove everything else that's punctuation/symbol *except* the three we already handled.
  # We explicitly exclude: apostrophe ' , hyphen - , and (already handled) period .
  x <- stringr::str_replace_all(
    x,
    "[!\"#$%&()*+,/:;<=>?@\\[\\]^_`{|}~\\\\„]",  # common ASCII punct & backslash
    " "
  )

  # Final tidy-up whitespace
  x <- stringr::str_squish(x)
  x
}

# ---- Abbreviation maps  ("yo" = "year old", etc.) ----
# For prose (description & on-screen text): multi-word expansions allowed
.abbr_map_text <- list(
  "\\byr\\b" = "year",
  "\\byo\\b" = "year old",
  "\\bsa\\b" = "sexual assault",
  "\\btw\\b" = "trigger warning",
  "\\bpt\\b" = "part"
)

# For hashtags (must remain one token; use hyphens for readability)
.abbr_map_hashtag_tokens <- c(
  "yr" = "year",
  "yo" = "year-old",
  "sa" = "sexual-assault",
  "tw" = "trigger-warning"
)

# ---- Expand abbreviations in *prose* fields ----
expand_abbreviations_text <- function(x, map = .abbr_map_text) {
  if (is.null(x)) return(x)
  x <- as.character(x)
  # Apply each pattern case-insensitively, respecting word boundaries
  for (pat in names(map)) {
    x <- stringr::str_replace_all(x, stringr::regex(pat, ignore_case = TRUE), map[[pat]])
  }
  # Clean up any excess spaces that expansions may introduce
  stringr::str_squish(x)
}

# ---- Expand abbreviations in *hashtag token* vectors ----
expand_abbreviations_hashtag_tokens <- function(tokens, map = .abbr_map_hashtag_tokens) {
  if (is.null(tokens) || length(tokens) == 0) return(tokens)
  # tokens are already lowercased in hashtag pipeline
  tokens <- ifelse(tokens %in% names(map), unname(map[tokens]), tokens)
  tokens
}

# ---- Normalize obfuscated "groom*" variants to ASCII "groom(+suffix)" ----
# Covers: groom, gr00m, gr0om, gro0m, gЯ00m, grоom (Cyrillic o), grοοm (Greek omicron),
#         grøm, gröm, gróm, and with suffixes: -ing/-ed/-s/-er/-ers
normalize_groom_variants <- function(x) {
  if (is.null(x)) return(x)
  x <- as.character(x)

  # Base+suffix pattern: either an obfuscated base or plain "groom", with an optional suffix
  pat <- paste0(
    "(?i)",                                   # case-insensitive
    "\\b(?:",
      "g(?:r|[\\x{042F}\\x{044F}])",          # 'r' or Cyrillic Я/я as 'r' spoof
      "(?:[o0\\x{043E}\\x{03BF}\\x{00D8}\\x{00F8}\\x{00F6}\\x{00F3}]){2}",  # o/0/homoglyphs x2
      "m",
      "|groom",                                # or just the plain word
    ")",
    "(ing|ed|s|er|ers)?",                      # capture suffix (if present)
    "\\b"
  )

  # Replace entire match with ASCII base + captured suffix
  stringi::stri_replace_all_regex(x, pat, "groom$1")
}

# (Optional) For hashtag token vectors; same behavior, vectorized over tokens
normalize_groom_in_tokens <- function(tokens) {
  if (is.null(tokens) || length(tokens) == 0) return(tokens)
  normalize_groom_variants(tokens)
}


# ---- Common text normalization pipeline (configurable) ----
normalize_text_common <- function(x,
                                  do_html_unescape = TRUE,
                                  do_strip_emojis  = TRUE,
                                  do_strip_zw      = TRUE,
                                  do_replace_urls  = TRUE,
                                  do_strip_hashtags= TRUE,
                                  do_strip_mentions= TRUE,
                                  do_restrict_punct= FALSE,
                                  do_expand_abbrev = FALSE,
                                  do_normalize_groom = TRUE,
                                  do_lower         = TRUE,
                                  do_squish        = TRUE) {
  if (is.null(x)) return(x)
  x <- as.character(x)

  # Unicode normalize first
  x <- stringi::stri_trans_nfc(x)
  if (do_html_unescape) x <- unescape_entities(x)
  if (do_strip_emojis)   x <- strip_emojis(x)
  if (do_strip_zw)       x <- strip_zero_width(x)
  if (do_replace_urls)   x <- replace_urls_with_placeholder(x)
  if (do_strip_hashtags) x <- strip_hashtag_tokens(x)
  if (do_strip_mentions) x <- strip_mentions(x)
  
  # Normalize "groom*" obfuscations before punctuation restriction
  if (do_normalize_groom) x <- normalize_groom_variants(x)
  
  # restrict punctuation
  if (do_restrict_punct) x <- restrict_punct_keep_contracts_hyphens_sentence_periods(x)

  # Whitespace + case + ASCII quotes
  if (do_squish) x <- stringr::str_squish(x)
  if (do_lower)  x <- stringi::stri_trans_tolower(x)
  
  # abbreviation expansion for prose fields  
  if (do_expand_abbrev) x <- expand_abbreviations_text(x)
  
  # Normalize any lingering curly quotes (defensive)
  x <- normalize_ascii_quotes(x)
  
  # Final squish in case expansions introduced spaces at ends  
  if (do_squish) x <- stringr::str_squish(x)

  x
}


```



```{r}
# === CHUNK 5.2: Clean & Normalize Hashtags ===
# Inputs:  meta$hashtags_list_raw (list; each row a vector or list of tags)
# Outputs: hashtags_list_clean (list<chr>),  hashtags_emoji (space-separated or NA)

stopifnot("hashtags_list_raw" %in% names(meta_dedup))

# Clean one vector of hashtags (no row expansion, returns character vector)
normalize_hashtags <- function(tags) {
  if (is.null(tags) || length(tags) == 0) return(character(0))

  # coerce & flatten
  tags <- as.character(unlist(tags, use.names = FALSE))

  # drop NAs, trim whitespace
  tags <- tags[!is.na(tags)]
  tags <- trimws(tags)

  # remove leading '#', allow accidental '##'
  tags <- sub("^#+", "", tags)

  # Unicode NFC + lowercase
  tags <- stringi::stri_trans_nfc(stringi::stri_trans_tolower(tags))

# strip all zero‑width chars (Unicode Cf category) to stabilize exact matches
tags <- gsub("\\p{Cf}", "", tags, perl = TRUE)

  # strip emojis + trim
  tags <- strip_emojis(tags)
  tags <- trimws(tags)

  # drop empties (e.g., after removing '#')
  tags <- tags[nzchar(tags)]
  
# expand abbreviations at token-level (keeps single-token hashtags)  
  tags <- expand_abbreviations_hashtag_tokens(tags)
  # normalize grooming variants
  tags <- normalize_groom_in_tokens(tags)

  # de-duplicate, preserve first occurrence order
  if (length(tags) > 1) tags <- tags[!duplicated(tags)]
  tags
}

# Extract emojis from raw hashtag list (kept as flat, space-separated string; NA if none)
extract_emojis_from_hashtag_list <- function(x) {
  if (is.null(x) || length(x) == 0) return(NA_character_)
  v <- as.character(unlist(x, use.names = FALSE))
  em <- stringi::stri_extract_all_regex(v, emoji_pat) |> unlist(use.names = FALSE)
  em <- em[!is.na(em)]
  if (length(em) == 0) NA_character_ else paste(em, collapse = " ")
}

    
meta_dedup <- meta_dedup %>%
  mutate(
    hashtags_list_clean = purrr::map(hashtags_list_raw, normalize_hashtags),
    hashtags_emoji      = purrr::map_chr(hashtags_list_raw, extract_emojis_from_hashtag_list),

    # exportable character column (compact JSON). 
    hashtags_clean      = purrr::map_chr(
      hashtags_list_clean,
      ~ if (length(.x) == 0) "[]" else jsonlite::toJSON(.x, auto_unbox = TRUE)
    )
  )

```



```{r}
head(meta_dedup$hashtags_list_clean)
```



```{r}
# === CHUNK 5.3, Clean On-Screen Text ===
## (1) remove the literal //n characters
## (2) flatten any strings that look like R’s c("…", "…") vector printout into plain text (joined with a single space)

# Input:  meta_dedup$on_screen_text_text (character)
# Output: on_screen_text_clean (character) + on_screen_text_emoji (space-separated or NA)

stopifnot("on_screen_text_text" %in% names(meta_dedup))

# Helper: flatten strings that look like R's c("…", "…") printout
flatten_c_printout <- function(x) {
  if (is.null(x)) return(x)
  x <- as.character(x)

  x %>%
    str_replace_all(fixed("//n"), "") %>%          # remove literal //n token
    str_replace_all("^\\s*c\\s*\\(\\s*", "") %>%   # drop leading c( (optional spaces)
    str_replace_all("\\s*\\)\\s*$", "") %>%        # drop trailing )
    str_replace_all(fixed("\\n"), " ") %>%         # literal backslash-n to space
    str_replace_all("[\\\"“”]", "") %>%            # remove all double quotes (ASCII + curly)
    str_replace_all("\\\\+", "") %>%               # drop stray backslashes
    str_replace_all("[\\r\\n]+", " ") %>%          # collapse real CR/LF to space
    str_replace_all("\\s*,\\s*", " ")              # commas (from c(..., ...)) -> space
}

meta_dedup <- meta_dedup %>%
  mutate(
    .on_text_raw = as.character(on_screen_text_text),

    # Emoji extraction from the raw field (for parity with desc)
    on_screen_text_emoji = extract_emojis_char(.on_text_raw),

    # First, flatten/straighten the printout format; then apply the common normalizer
    on_screen_text_clean = .on_text_raw %>%
      flatten_c_printout() %>%
      normalize_text_common(
        do_html_unescape  = TRUE,
        do_strip_emojis   = TRUE,
        do_strip_zw       = TRUE,
        do_replace_urls   = TRUE,
        do_strip_hashtags = TRUE,   
        do_strip_mentions = TRUE,
        do_restrict_punct = TRUE, 
        do_expand_abbrev  = TRUE,
        do_normalize_groom = TRUE,
        do_lower          = TRUE,
        do_squish         = TRUE
      )
  ) %>%
  select(-.on_text_raw)


#Check
head(meta_dedup$on_screen_text_clean)
```


```{r}
# === CHUNK 5.4, Clean Description ===

# Input:  meta_dedup$desc_raw (character)
# Output: desc_clean (character) + desc_emoji (space-separated or NA)

stopifnot("desc_raw" %in% names(meta_dedup))

meta_dedup <- meta_dedup %>%
  mutate(
    .desc = as.character(desc_raw),

    # Extract emojis (space-separated; NA if none)
    desc_emoji = extract_emojis_char(.desc),

    # Apply the common normalization pipeline
    desc_clean = .desc %>%
      normalize_text_common(
        do_html_unescape  = TRUE,
        do_strip_emojis   = TRUE,
        do_strip_zw       = TRUE,
        do_replace_urls   = TRUE,
        do_strip_hashtags = TRUE,
        do_strip_mentions = TRUE,
        do_restrict_punct = TRUE, 
        do_expand_abbrev  = TRUE,
        do_normalize_groom = TRUE,
        do_lower          = TRUE,
        do_squish         = TRUE
      )
  ) %>%
  select(-.desc)

# (optional) quick confirmation
cat(
  "desc_raw non-NA: ", sum(!is.na(meta_dedup$desc_raw)),
  "\n",
  "desc_clean non-NA: ", sum(!is.na(meta_dedup$desc_clean)),
  "\n",
  "with emojis found: ", sum(!is.na(meta_dedup$desc_emoji)),
  "\n", sep = ""
)


head(meta_dedup$desc_clean)

```

```{r}
################# EXPORT ################# 

# TRUE = list/packed; FALSE = flat/scalar (exportable)
is_list_col <- map_lgl(meta_dedup, is.list)

packed_cols     <- names(meta_dedup)[is_list_col]
exportable_cols <- names(meta_dedup)[!is_list_col]

# Quick peek
packed_cols
exportable_cols

meta_dedup_export <- meta_dedup %>% select(all_of(exportable_cols))
```

```{r}
writexl::write_xlsx(meta_dedup_export, "meta_sans_trans.xlsx")
```















